\chapter{Background}
\section{The Game Name}
I started to play pen and paper fantasy role play games with Shadowrun and DSA (a German system, could be translated as The Dark Eye).  The Runny Eye is a mixture of both titles in a way where I feel comfortable not to hurt any heavily protected trademark, even without doing a lot of research.

\section{Inspiration}
The basic concepts are heavily influenced by Terry Pratchett's ideas. If you create a new archetype and you read some disk-world novels first, it will probably help. But there are also strong differences between his ideas and the concepts of this game: I do not invent my own landscape (or copy the one he created for disk-world). The geography in this concept is surprisingly similar to the one on earth, to make it easy to use real maps to plan your adventures. Also, we have some strict rules, because sometimes it is easier to solve disputes that way.

While I loved the games themselves, I despised the fact, that they where strictly commercial. The rule-sets where company controlled, sometimes community websites were discontinued because they violated the owners intellectual property, or software written by enthusiasts was withdrawn or half-illegal. While I do understand that companies need to earn, in the area of fantasy role-play where every game master and even every single contributes a lot of ideas and creativity the limitations just felt wrong. Another issue was that while the material to play the game is really minimalistic (pen, paper and some dice), it is artificially kept expensive by introducing special maps, new spell-books, etc.
\\
For my game I will not include every proposed idea, since I have my own plans what the game should be like. But everyone is heartily invited to fork this project under some copyleft license and add his ideas under that license for himself.

