\chapter{Background}
\section{Motivation}
I started to play pen and paper fanasy roleplay games with Shadowrun and DSA (a German system, could be translated as The Dark Eye). While I loved the games themselfe, I despised the fact, that they where strictly commercial. The rulesets where company controlled, sometimes community websites were discontinued becuase they violated the owners intellectual property, or software written by enthusiasts was withdrawn or half-illegal. While I do understand that companies need to earn, in the area of fantasie roleplay where every game master and even every single contributes a lot of ideas and creativity it just felt wrong. Another issue was that while the material to play the game is really minimalistic (pen, paper and some dice), it is artificially kept expensive by introducing special maps etc.
\\
For my game I will not include every proposed idea, since I have my own plans what the game should be like. But everyone is heartly invided to fork this project under 
some copyleft license and include his ideas under that license for himself.

\section{Inspiration}
The basic concepts are heavily influenced by Terry Pratchetts ideas. If you create a new archetype and you read some diskworld novels first, it will probably help. But there are also strong differences between his ideas and the concepts of this game: I do not invent my own landscape (or copy the one he created for diskworld). The geography in this concept is surprisingly similar to the one on eartch, to make it easy to use real maps to plan your adventures. Also, we have some strict rules, because sometimes it is easier to solve disputes that way.
